```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}

opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=FALSE, tidy=TRUE, fig.keep='high', echo=TRUE, dpi=300, out.width=700, prompt=FALSE, comment='##', results='markup', eval=FALSE)
# See yihui.name/knitr/options for more Knitr options.
```

server, a module to run web interface
========================================================

Before starting the web server, ensure you've created the [database](../dbcreator/dbcreator.md) and have at least one  [background file](../dbcreator/dbcreatorBackground.md).

We start the web interface as:

```{r}
python -m grsnp.server -g hg19 -d [dir1],[dir2],[dir3] -r [dir1]
```

where the **-d** parameter accepts a single or comma-separated *full paths* to the databases. The **-r** parameter specifies the path to the `results` folder.

Access GenomeRunner on [http://localhost:8000/gr/](http://localhost:8000/gr/). 

The `server` module should create a log file (genomerunner_server.log) in the `[dir]` folder - study it for troubleshooting.