```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}

opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=FALSE, tidy=TRUE, fig.keep='high', echo=TRUE, dpi=300, out.width=700, prompt=FALSE, comment='##', results='markup', eval=FALSE)
# See yihui.name/knitr/options for more Knitr options.
```

Custom data
============

Custom features of interest (FOIs)
-----------------------------

Sometimes we may want to have sets of features of interest readily accessible for the analysis, such as demo sets, or sets of random features. We may place the BED files with genomic coordinates of such FOIs in the subfolders under the `[dir]/custom_data/fois/[organism]/` folder. The names of the subfolders serve as descriptions of the sets of FOIs.

An example of the `fois` folder may look like:

```{r}
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/fois/hg19/GWAStest1/*.bed
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/fois/hg19/GWASrand/*.bed
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/fois/hg19/SNPsCommonRand/*.bed
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/fois/hg19/GWAScatalogFull/*.bed
```

Custom genomic features (GFs)
-----------------------

Some genome annotation tracks contain information about different biologically relevant features, combined together. An example of such combined table is the `wgEncodeRegTfbsClusteredV3` track, containing experimentally detected transcription factor binding sites for 161 different transcription factors. We may want to consider the data for each transcription factor separately. We process such combined data using the `extract_UCSC.py` script (see the `db` subfolder in the [source code](https://github.com/mdozmorov/genome_runner) folder). We place extracted BED files in the `[dir]/custom_data/gfs/hg19/tfbsEncode` folder. The `tfbsEncode` GFs will be accessible through GenomeRunner's web interface.

It is a good idea to remove special characters from file names, if any, by running:

```{r}
for FILE in *.bed; do mv -v "$FILE" echo $FILE | tr ' ' '_' | tr -d '[{}(),!]' | tr -d "'" | tr '[A-Z]' '[a-z]' | sed 's/_-_/_/g';done
```

An example of the `gfs` folder may look like:

```{r}
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/gfs/hg19/tfbsEncode/*.bed
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/gfs/hg19/H3K4me3/*.bed
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/gfs/hg19/gwasCatalog/*.bed
/home/testuser/Documents/db_1.01_05.12.2014/custom_data/gfs/hg19/chromStates/*.bed
```


Random sets of FOIs
--------------------

Any scientific experiment testing for presence of an effect should include a positive control, that is, a condition known to lack an effect. In case of GenomeRunner, we should use randomly selected SNP set of the same size as the FOIs themselves. That is, we are testing:

1) A set of FOIs, e.g., 100 disease-associated SNPs - we expect to find biologically relevant enrichments
2) A random set, e.g., 100 randomly selected SNPs - we expect them to show no significant enrichments

Random sets of SNPs should be generated from the background:

```{r}
zcat [dir]/custom_data/backgrounds/[org]/3gwasCatalog.bed.gz | shuf | head -n 100 > rndgwascatalog_100.bed
```

To generate multiple random sets of SNPs of different sizes, use:

```{r}
for i in {7..13}; do c=$(awk "BEGIN{print 2 ** $i}"); zcat 3gwasCatalog.bed.gz | shuf | head -n $c > rndgwasCatalog_$c.bed; done
```

It will generate 7 sets of randomly selected SNPs of the sizes of power of 2 (128 SNPs, 256, etc.).
