```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}

opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=FALSE, tidy=TRUE, fig.keep='high', echo=TRUE, dpi=300, out.width=700, prompt=TRUE, comment='##', results='markup', eval=FALSE)
# See yihui.name/knitr/options for more Knitr options.
```

How dbcreator works
========================================================

The dbcreator performs several steps:

* Downloads required files from USCS and places them in `[dir]/downloads/`. Note that this step may take several days on slow connections. If the download process fails, simply re-run dbcreator - this will resume the process.

* Converts the files into [the BED format](http://genome.ucsc.edu/FAQ/FAQformat.html#format1), sorts them according to the USCS schema, compresses with [bgzip](http://samtools.sourceforge.net/tabix.shtml). Unsupported data formats are skipped, with warning.

* Places the converted files in `[dir]/grsnp_db/[organism code]/[group]`. The ENCODE data (tracks beginning with wgEncode) are placed in separate ENCODE subfolders, strictured as `[dir]/grsnp_db/[organism]/ENCODE/[data source/type]/[Tier]/[cell type]`.

After the database has been created, the bgzip'ed files need to be indexed with with tabix

```{r}
cd [dir]
find . -type f -name '*.bed.gz' -exec tabix {} \;
```

Fixme: Automate this into dbcreator